Demographic Groups with Stronger Biden Support in the Election Race

### 2024-04-04 paper/paper.qmd
update change

```{r}
#| label: fig-vote
#| fig-cap: The distribution of presidential preferences, by education, and gun ownership
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-vote
#| fig-cap: The distribution of presidential preferences, by education, and gun ownership
#| echo: false
#| warning: false
#| message: false

@@

```
```{r}
#| label: fig-vote
#| fig-cap: The distribution of presidential preferences, by education, and gun ownership
#| echo: false
#| warning: false
#| message: false

@@

>>>>

```{r}
#| label: fig-income-vote
#| fig-cap: The distribution of presidential preferences, by income level
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-education-vote
#| fig-cap: The distribution of presidential preferences, by education
#| echo: false
#| warning: false
#| message: false

@@

```
```{r}
#| label: fig-gun-ownership-vote
#| fig-cap: The distribution of presidential preferences, by gun ownership
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-education-income-vote
#| fig-cap: The distribution of presidential preferences, by education, and income level
#| echo: false
#| warning: false
#| message: false
